Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-19 README.Rmd
updated readme and trying to get binder going
still trying to get binder working + docker

# robinson2020

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio)

@@

**Code :** See the [LICENSE](LICENSE.md) file

@@

This compendium was created using the `rrtools` package by Ben Marwick: []()

>>>>

# robinson2020
[![Travis-CI Build Status](https://travis-ci.org/bocinsky/robinson2020.svg?branch=master)](https://travis-ci.org/bocinsky/robinson2020)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio)

@@

**Code :** [GNU GPLv3](LICENSE.md)

@@

This compendium was created using the [`rrtools` package by Ben Marwick](https://github.com/benmarwick/rrtools), which is ✨pure magic ✨for doing reproducible research.
